---
title: "Scenarios with K_LINFcvp2, Stock Synthesis EM runs"
author: "Kathryn Doering"
date: "6/24/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Description of simulation runs

100 simulations of 4 different OM scenarios were run:


```{r }
# fixed values ----
mydir <- getwd()
outer_folder <- file.path(mydir, "Scenarios")
outer_folder_output <- file.path(mydir, "output", basename(outer_folder))
cases <- list.dirs(outer_folder_output, full.names = FALSE, recursive = FALSE)
run_date <-  "2021_06_24"
print(cases)
```
For each of the OM Scenarios, there were 100 data sets, so each iteration of a scenario used a different dataset from the OM.

For each OM scenario, 2 SS estimation models were run: one that used 5 platoons and one that only had 1 platoon. Stock Synthesis version 3.30.16 was used for the runs, but we could update to 3.30.17.

After the SS models were run, they were summarized into CSV files for different model quantities.

## Setup results

```{r, results="hide", warning=FALSE, message=FALSE}
# load pkgs, set options -----
library(r4ss)
source(file.path(mydir, "code", "SS_run_functions.R"))
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)

Rdata_folder <- file.path(mydir, "Rdata_output", basename(outer_folder))
```

Read in the csv files generated from the runs, and add as components of a list of lists:
```{r}
# read in csv files ----
csv_list <- lapply(cases, function(icase, outer_folder) {
  mydir.dat <- file.path(outer_folder, icase)
  out_ab <- file.path(mydir.dat, '../ResultsSSab')
  out_pl <- file.path(mydir.dat, '../ResultsSSpl')
  partable_plat <- read.csv(file.path(out_pl, "SS_parameters.csv"))
  partable_noplat <- read.csv(file = file.path(out_ab, "SS_parameters.csv"))
  recruits_plat <- read.csv(file = file.path(out_pl, "SS_recruitment.csv"))
  recruits_noplat <- read.csv(file.path(out_ab, "SS_recruitment.csv"))
  F_plat <- read.csv(file.path(out_pl, "SS_exploitation.csv"))
  F_noplat <- read.csv(file.path(out_ab, "SS_exploitation.csv"))
  N30plus_plat <- read.csv(file.path(out_pl, "SS_numbers30plus.csv"))
  N30plus_noplat <- read.csv(file.path(out_ab, "SS_numbers30plus.csv"))
  B30plus_plat <- read.csv(file.path(out_pl, "SS_biomass30plus.csv"))
  B30plus_noplat <- read.csv(file.path(out_ab, "SS_biomass30plus.csv"))
  plat_list <- list(partable = partable_plat,
                    recruits = recruits_plat, 
                    F_val = F_plat, 
                    N30plus = N30plus_plat, 
                    B30plus = B30plus_plat)
  noplat_list <- list(partable = partable_noplat,
                    recruits = recruits_noplat, 
                    F_val = F_noplat, 
                    N30plus = N30plus_noplat, 
                    B30plus = B30plus_noplat)
  val_list <- list(platoons = plat_list,
                   no_platoons = noplat_list)
  val_list
}, outer_folder = outer_folder)
names(csv_list) <- cases # 1 list per case; within each case list, each csv file is a list of components
```
## Check convergence of models

Get the parameter tables:
```{r}
# look at iterations that didn't converge ----

partbl_df_plat <- mapply(make_plotting_df,
                         scen_list = csv_list, scen_name = names(csv_list), 
                         MoreArgs = list(platoons = TRUE, metric = "partable"),
                         SIMPLIFY = FALSE)
partbl_df_noplat <- mapply(make_plotting_df,
                           scen_list = csv_list, scen_name = names(csv_list), 
                           MoreArgs = list(platoons = FALSE, metric = "partable"),
                           SIMPLIFY = FALSE)
partbl_df_plat <- do.call(rbind, partbl_df_plat)
partbl_df_noplat <- do.call(rbind, partbl_df_noplat)
partbl_df <- rbind(partbl_df_plat, partbl_df_noplat)
head(partbl_df)

```

Now, find which iterations didn't converge:
```{r}
# create table so can remove non converged runs from the other datasets.
not_converged <- partbl_df[partbl_df$converged == FALSE, c("run", "scen", "platoons")]
rownames(not_converged) <- as.character(1:nrow(not_converged))
not_converged
```
There were a total of `r nrow(not_converged)` iterations total that didn't converge, all of which were models with platoons. Looking more into this, I think these model runs exited on error for some reason.

Also, remove the non-converged iterations from `partbl_df` before plotting:

```{r}
partbl_df <- partbl_df[partbl_df$converged == TRUE, ]
```

## Plots and descriptions of quantities from the EMs

### Plots of the parameter values:
```{r}
partbl_long <- gather(partbl_df, key = "parameter", value = "value", 4:9)

ggplot(partbl_long, aes(x = scen, y = value)) +
  geom_boxplot(aes(fill = platoons))+
  scale_fill_brewer(palette = "Set2")+
  facet_wrap(~parameter, scales = "free_y")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))
```

Note that CV_old seems to be hitting a bound in some of the scenarios, so we may need to consider re-running these after changing the bound within the SS EM (I think the true value was 0.20)?

Overall, there are differences between platoons and no platoons runs. Likewise, the relationship between Linf and K is shifted down for no platoon runs compared to platton runs:

```{r}
ggplot(partbl_df, aes(x = K, y = Linf_mm)) +
  geom_point(aes(color = platoons))+
  scale_color_brewer(palette = "Set2")+
  facet_wrap(~scen)+
  theme_classic()
```

### Other quantities

Other quantities were extracted from `csv_list` and the non-converged iterations were removed.

Plots of fishing mortality, first a spaghetti plot showing all runs:
```{r, F-plots, echo = FALSE}
F_df_plat <- mapply(make_plotting_df,
                    scen_list = csv_list, scen_name = names(csv_list), 
                    MoreArgs = list(platoons = TRUE, metric = "F_val"),
                    SIMPLIFY = FALSE)
F_df_noplat <- mapply(make_plotting_df,
                       scen_list = csv_list, scen_name = names(csv_list), 
                       MoreArgs = list(platoons = FALSE, metric = "F_val"),
                       SIMPLIFY = FALSE)
F_df_plat <- do.call(rbind, F_df_plat)
F_df_noplat <- do.call(rbind, F_df_noplat)
F_df <- rbind(F_df_plat, F_df_noplat)

iter_cols <- grep("replist", colnames(F_df))
F_df_long <- gather(F_df, "iteration", "F_val", all_of(iter_cols)) %>% 
               separate(col = iteration, into = c(NA, "run"), sep = "list", 
                        remove = TRUE)
F_df_long$run <- as.integer(F_df_long$run)
# remove unconverged runs
F_df_long <- anti_join(F_df_long, not_converged)
F_df_long$run <- as.character(F_df_long$run)

ggplot(F_df_long, aes(x = Yr, y = F_val)) +
  geom_line(aes(color = platoons, linetype = run)) +
  facet_wrap(~scen) +
  scale_linetype_manual(values = rep("solid", times = length(iter_cols))) +
  scale_color_brewer(palette = "Set2")+
  guides(linetype = FALSE)+
  theme_classic()
```

Next, a plot of Fishing mortality showing a quick summary of runs:

```{r, echo=FALSE}
ggplot(F_df_long, aes(x = Yr, y = F_val)) +
  geom_smooth(aes(color = platoons)) +
  facet_wrap(~scen) +
  scale_color_brewer(palette = "Set2")+
  theme_classic()
```

Similar plots were made for other quantities.

Plots of Numbers of fish for fish >= 30 (unsure of units):

```{r echo=FALSE}

N_df_plat <- mapply(make_plotting_df,
                    scen_list = csv_list, scen_name = names(csv_list), 
                    MoreArgs = list(platoons = TRUE, metric = "N30plus"),
                    SIMPLIFY = FALSE)
N_df_noplat <- mapply(make_plotting_df,
                      scen_list = csv_list, scen_name = names(csv_list), 
                      MoreArgs = list(platoons = FALSE, metric = "N30plus"),
                      SIMPLIFY = FALSE)
N_df_plat <- do.call(rbind, N_df_plat)
N_df_noplat <- do.call(rbind, N_df_noplat)
N_df <- rbind(N_df_plat, N_df_noplat)

iter_cols <- grep("run", colnames(N_df))
N_df_long <- gather(N_df, "iteration", "N_val", all_of(iter_cols)) %>% 
  separate(col = iteration, into = c(NA, "run"), sep = "un", 
           remove = TRUE)
N_df_long$run <- as.integer(N_df_long$run)
# remove unconverged runs
N_df_long <- anti_join(N_df_long, not_converged)
N_df_long$run <- as.character(N_df_long$run)


ggplot(N_df_long, aes(x = Yr, y = N_val)) +
  geom_line(aes(color = platoons, linetype = run)) +
  facet_wrap(~scen) +
  scale_linetype_manual(values = rep("solid", times = length(iter_cols))) +
  scale_color_brewer(palette = "Set2")+
  guides(linetype = FALSE)+
  theme_classic()

ggplot(N_df_long, aes(x = Yr, y = N_val)) +
  geom_smooth(aes(color = platoons)) +
  facet_wrap(~scen) +
  scale_color_brewer(palette = "Set2")+
  theme_classic()
```


Plots of biomass for fish >= 30 (unsure of units):
```{r, biomass-plots, echo=FALSE}
B_df_plat <- mapply(make_plotting_df,
                    scen_list = csv_list, scen_name = names(csv_list), 
                    MoreArgs = list(platoons = TRUE, metric = "B30plus"),
                    SIMPLIFY = FALSE)
B_df_noplat <- mapply(make_plotting_df,
                      scen_list = csv_list, scen_name = names(csv_list), 
                      MoreArgs = list(platoons = FALSE, metric = "B30plus"),
                      SIMPLIFY = FALSE)
B_df_plat <- do.call(rbind, B_df_plat)
B_df_noplat <- do.call(rbind, B_df_noplat)
B_df <- rbind(B_df_plat, B_df_noplat)

iter_cols <- grep("run", colnames(B_df))
B_df_long <- gather(B_df, "iteration", "B_val", all_of(iter_cols)) %>% 
  separate(col = iteration, into = c(NA, "run"), sep = "un", 
           remove = TRUE)
B_df_long$run <- as.integer(B_df_long$run)
# remove unconverged runs
B_df_long <- anti_join(B_df_long, not_converged)
B_df_long$run <- as.character(B_df_long$run)

ggplot(B_df_long, aes(x = Yr, y = B_val)) +
  geom_line(aes(color = platoons, linetype = run)) +
  facet_wrap(~scen) +
  scale_linetype_manual(values = rep("solid", times = length(iter_cols))) +
  scale_color_brewer(palette = "Set2")+
  guides(linetype = FALSE)+
  theme_classic()

ggplot(B_df_long, aes(x = Yr, y = B_val)) +
  geom_smooth(aes(color = platoons)) +
  facet_wrap(~scen) +
  scale_color_brewer(palette = "Set2")+
  theme_classic()
```

Plots of recruits (numbers?):
```{r echo=FALSE}
recruits_df_plat <- mapply(make_plotting_df,
                    scen_list = csv_list, scen_name = names(csv_list), 
                    MoreArgs = list(platoons = TRUE, metric = "recruits"),
                    SIMPLIFY = FALSE)
recruits_df_noplat <- mapply(make_plotting_df,
                      scen_list = csv_list, scen_name = names(csv_list), 
                      MoreArgs = list(platoons = FALSE, metric = "recruits"),
                      SIMPLIFY = FALSE)
recruits_df_plat <- do.call(rbind, recruits_df_plat)
recruits_df_noplat <- do.call(rbind, recruits_df_noplat)
recruits_df <- rbind(recruits_df_plat, recruits_df_noplat)

iter_cols <- grep("replist", colnames(recruits_df))
recruits_df_long <- gather(recruits_df, "iteration", "recruits", all_of(iter_cols)) %>% 
  separate(col = iteration, into = c(NA, "run"), sep = "list", 
           remove = TRUE)
# remove unconverged runs
recruits_df_long$run <- as.integer(recruits_df_long$run)
recruits_df_long <- anti_join(recruits_df_long, not_converged)
recruits_df_long$run <- as.character(recruits_df_long$run)

ggplot(recruits_df_long, aes(x = Yr, y = recruits)) +
  geom_line(aes(color = platoons, linetype = run)) +
  facet_wrap(~scen) +
  scale_linetype_manual(values = rep("solid", times = length(iter_cols))) +
  scale_color_brewer(palette = "Set2")+
  guides(linetype = FALSE)+
  theme_classic()

ggplot(recruits_df_long, aes(x = Yr, y = recruits)) +
  geom_smooth(aes(color = platoons)) +
  facet_wrap(~scen) +
  scale_color_brewer(palette = "Set2")+
  theme_classic()
```

## TODO

Investigate the few models that still have params on bounds




